---
title: "project_2"
output: html_document
---



```{r}
kc_house_data <- read.csv("~/Downloads/kc_house_data.csv", header=T)
library(rpart)
library(caret)
library(ggplot2)
library(GGally)
library(dplyr)
View(kc_house_data)
```
# Convert Date format for regression
```{r}
kc_house_data$date <- (substr(kc_house_data$date,1,8))
kc_house_data$date <- ymd(kc_house_data$date)
kc_house_data$date<-as.numeric(as.Date(kc_house_data$date, origin = "1900-01-01"))

```

## Checking Relationship between price, date,bedrooms, bathrooms, sqft_living and sqft lot
```{r}
plot1<- ggpairs(data=kc_house_data, columns=c(3,2,4:7),mapping = aes(color = "blue"),axisLabels="show")
plot1
```
## Checking Relationship between price, floors, waterfront, view, condition,grade,sqft_above,sqft_basement,yr_built
```{r}
plot2<-ggpairs(data=kc_house_data, columns=c(3,8:15),mapping = aes(color = "blue"),axisLabels = "show")
plot2
```

## Checking Relationship between price,yr_renovated,zipcode,lat,long,sqft_living15,sqft_lot15
```{r}
plot3<-ggpairs(data=kc_house_data, columns=c(3,15:21),mapping = aes(color = "blue"),axisLabels = "show")
plot3

```

# Linear Regression
```            {r  #Set up Cross validation} 
library(caret)
set.seed(100)
indx <- createFolds(y=kc_house_data$price,k=10,returnTrain=TRUE)
ctrl <- trainControl(method="cv",index=indx)
```

```{r}
set.seed(100)
lmTune0 <- train(x= kc_house_data[,-c(1,3)],y=kc_house_data$price,method="lm",trControl = ctrl)
lmTune0
summary(lmTune0)
```



## Recursive Partitioning
```{r}
set.seed(123)
ctrl = trainControl(method="cv", number = 10)
cartTune <- train(x= kc_house_data[,-c(1,3)],y=kc_house_data$price,method = "rpart",tuneLength = 25,trControl = ctrl)
cartTune
cartTune$finalModel
plot(cartTune, scales = list(x = list(log = 10)))
```



# Ridge Regression

```{r}
ridgeGrid <- expand.grid(lambda = seq(0, 0.1, by = 0.005))
set.seed(100)
ridgeTune <- train(x= kc_house_data[,-c(1,3)],y=kc_house_data$price,method ="ridge",tuneGrid = ridgeGrid,trControl = ctrl,preProc = c("center", "scale"))
ridgeTune
print(update(plot(ridgeTune), xlab = "Penalty"))
```

## Principle Component Analysis

```{r}
set.seed(100)
pcrTune <- train(x= kc_house_data[,-c(1,3)],y=kc_house_data$price,method = "pcr",tuneGrid = expand.grid(ncomp = 1:19),trControl = ctrl)
pcrTune
pcrImp <- varImp(pcrTune, scale = FALSE)
plot(pcrImp, top = 10, scales = list(y = list(cex = .95)))
```
## Partial Least Squares

```{r}
set.seed(100)
plsTune <- train(x= kc_house_data[,-c(1,3)],y=kc_house_data$price,method = "pls",tuneGrid = expand.grid(ncomp = 1:19),trControl = ctrl)
plsTune
plsImp <- varImp(plsTune, scale = FALSE)
plot(plsImp, top = 10, scales = list(y = list(cex = .95)))
```
